This section provides the reader with an overview of the SCARA Robot Arm. The primary operational aspects of the product, from the perspective of end users, maintainers and administrators, are defined here. The key features and functions found in the product, as well as critical user interactions and user interfaces are described in detail.

\subsection{Features \& Functions}
The SCARA Robot Arm will perform the actions of recognition of user defined object within groups of objects of different shapes, sizes, colors where the Arm will extract the desired object and place it in a designated sorting bin attached to the SCARA Robot Arm's base.

The principal parts of the SCARA Robot Arm consist of two separate arm segments which separately pivot 270 degrees fixed atop the  mounting base attached to the 18 inch x 18 inch work area. Each arm segment  is 12 inches in length with a pivot point on each end. 

Movement for the SCARA Robot Arm is handled by 2 Nema 23 stepper motors, one in the base assembly on the rotational axis for the first segment and the second mounted above the axis of the rotation point for the first arm segment located on the axis of the base assembly. The end effector's vertical movement's responsibility is handled by an Linear Actuator with a lead screw design type. 

\subsection{External Inputs \& Outputs}

Describe critical external data flows. What does your product require/expect to receive from end users or external systems (inputs), and what is expected to be created by your product for consumption by end users or external systems (outputs)? In other words, specify here all data/information to flow into and out of your systems. A table works best here, with rows for each critical data element, and columns for name, description and use.

\subsection{Product Interfaces}
Operational interfaces will have a organized, functional, uncluttered appearance for all types of users. User interface types shall be restricted to user and maintainer. The user interface shall be for all use of the SCARA Robot Arm to perform all processes desired. The maintainer interface shall be for the introductory set up and calibration of the SCARA Robot Arm and for any other calibration needs post setup. 

Specify what all operational (visible) interfaces look like to your end-user, administrator, maintainer, etc. Show sample/mocked-up screen shots, graphics of buttons, panels, etc. Refer to the critical external inputs and outputs described in the paragraph above.
